MCC Informativeness Kids

### 2018-07-30 stats/mcc_inf.kids.Rmd
add new info exp version
adding new kids inforamtiveness experiment

We reached the pre-registered sample size for 3yo, that's why I took another look at the data. See below the nr. of subjects we have so far.

@@

d %>%
  group_by(age)%>%
  summarise(n = length(unique(subid)))%>%
  knitr::kable(digits = 2)
```

@@

We can ignore this plot for now and go straight to the plot by age bin as we are primarily interested in the 3yo.

>>>>

@@

d %>%
  group_by(age)%>%
  summarise(n = length(unique(subid)))%>%
  knitr::kable(digits = 2)

@@
